Predicting Kamala Harris's Victory in the 2024 US Election

### 2024-10-25 paper/paper.qmd
Add reference bib.

We expect a positive relationship between the size of the wings and time spent aloft. In particular...

We can use maths by including latex between dollar signs, for instance $\theta$.

@@

```{r}

library(caret)
set.seed(856)
train_control <- trainControl(method = "cv", number = 10)
cv_model <- train(percent ~ numeric_grade + sample_size + state + transparency_score + end_date,
                  data = analysis_data_train,
                  method = "lm",
                  trControl = train_control)

@@

```{r}
baseline_prediction <- mean(analysis_data_train$percent)
baseline_mse <- mean((analysis_data_test$percent - baseline_prediction)^2)
print(baseline_mse)
```

```{r}
# Calculate R-squared on test data
rss <- sum((predicted_values - actual_values)^2)  # Residual Sum of Squares
tss <- sum((actual_values - mean(actual_values))^2)  # Total Sum of Squares

@@

```{r}
# Create a correlation matrix to check for collinearity
cor_matrix <- cor(analysis_data_train[, c("numeric_grade", "sample_size", "transparency_score")], use = "complete.obs")
print(cor_matrix)
```
```{r}
# Check for sparse levels in 'state'
state_counts <- table(analysis_data_train$state)
print(state_counts)
```

@@

# Acknowledgements
@citeR
Thanks to Open AI [@openai2024chatgpt] and ChatGPT 4.0 is used to write the analysis of the paper.

>>>>

@@

```{r}
#| echo: false
library(caret)
set.seed(856)
train_control <- trainControl(method = "cv", number = 10)
cv_model <- train(percent ~ numeric_grade + sample_size + state + transparency_score + end_date,
                  data = analysis_data_train,
                  method = "lm",
                  trControl = train_control)

@@

```{r}
#| echo: false
baseline_prediction <- mean(analysis_data_train$percent)
baseline_mse <- mean((analysis_data_test$percent - baseline_prediction)^2)
print(baseline_mse)
```

```{r}
#| echo: false
# Calculate R-squared on test data
rss <- sum((predicted_values - actual_values)^2)  # Residual Sum of Squares
tss <- sum((actual_values - mean(actual_values))^2)  # Total Sum of Squares

@@

```{r}
#| echo: false
# Create a correlation matrix to check for collinearity
cor_matrix <- cor(analysis_data_train[, c("numeric_grade", "sample_size", "transparency_score")], use = "complete.obs")
print(cor_matrix)
```

```{r}
#| echo: false
# Check for sparse levels in 'state'
state_counts <- table(analysis_data_train$state)
print(state_counts)
```

@@

# Acknowledgements
@citeR
Thanks to Open AI and ChatGPT 4.0 is used to write the analysis of the paper.

@fivethirty provides the data. @tidyverse, @ggplot, @knitr
